---
title: "Add a Slack Login to a shiny app"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Add a Slack Login to a shiny app}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

The shinyslack package makes it easy to add a Slack login to a shiny app.

Imagine you have a shiny app in an `app.R` file.

```{r basic-shiny}
library(shiny)
ui <- fluidPage(
  "This is my super secret data."
)
server <- function(input, output, session) {
}
shinyApp(ui, server)
```

`{shinyslack}` makes it easy to require a Slack login before the user can view that app.
Simply replace the call to `shinyApp()` with a call to `shiny_slack_app()`.

```{r basic-shinyslack}
library(shiny)
library(shinyslack)
ui <- fluidPage(
  "This is my super secret data."
)
server <- function(input, output, session) {
}
shiny_slack_app(
  ui, server, 
  team_id = "T6UC1DKJQ", 
  site_url = "https://myaccount.shinyapps.io/myapp/"
)
```

The `site_url` is only necessary if you deploy your app.
The login workflow needs this url to know where to send the user back to after logging in.

## Finding your team_id

The `team_id` shown here is the ID for the [R4DS Online Learning Community Slack](r4ds.io/join).
You can find your `team_id` in a few ways:

- Open your Slack team in a web browser. The url will display as something like `https://app.slack.com/client/T6UC1DKJQ/C8J63E0TA`, where the string immediately after `client/` is your `team_id`.
- In the Slack desktop app, click the name of your team at the top-left corner of the app. Choose the first link below the team name, which will say something like "See plans". The url will be something like `https://app.slack.com/plans/T6UC1DKJQ`, where the string after `plans/` is your `team_id`.

